Tutorial_2b

### 2024-11-24 Tutorial_2a.Rmd
update tuts 2a and 2b

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r}
plan(multicore)

@@

@@

```{r ppc-M0i-prior}
# Generate prior predictive hazard functions for 6 participants
newdata_prior = tibble(timebin = 6:15) %>% 
           expand_grid(pid = 1:6)

@@

```{r insppect-M0i}
model_M0i <- readRDS("Tutorial_2_Bayesian/models/model_M0i.rds")
summary(model_M0i)
formula(model_M0i)
plot(model_M0i)
```

@@

@@

```{r ppc-model-M0c-prior}
# Generate prior predictive hazard functions for 6 participants
# Specify
N_obs = 100 # increase for smoother results
set.seed(1)

@@

```{r}
post <- as_draws_df(model_M1i) %>% 
  select(-lp__) %>% 
  as_tibble()

@@

```{r}
tidy_fixed <- post %>% 
  select(starts_with("b_"), .chain, .iteration, .draw) %>% 
  rename(chain=.chain, iter=.iteration, draw=.draw) %>% 
  pivot_longer(-c(chain, draw, iter)) %>% 
  mutate(timebin = str_sub(name,10,11),
         timebin = factor(str_remove(timebin,":"),levels=c(6:15)),
         condition = str_sub(name,17,18),
         condition = factor(str_remove(condition,"e"),
                            levels=c(1,2,3),
                            labels=c("blank","congruent","incongruent")))
head(tidy_fixed)
tail(tidy_fixed)

@@

```{r save-post, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pred_grand.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-post, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pred_pid.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-post, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pred_pid_new.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-post, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_grand_AME.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-post, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pid_AMEs.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-post, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pid_new_AMEs.png", width = 10, height = 8, dpi = 800)
```

@@

```{r}
pabove <- epreds_grand_diffs %>% 
  group_by(timebin,contrast) %>%
  summarize(prop_above = mean(pred_haz > 0)) %>% 
  arrange(contrast,timebin)

>>>>

```{r setup, include=FALSE, results='hide'}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r M0i-prior, eval=F}
plan(multicore)

@@

```{r inspect-M0i-prior}
model_M0i_prior <- readRDS("Tutorial_2_Bayesian/models/model_M0i_prior.rds")
```

@@

```{r ppc-M0i-prior, eval=F}
# Generate prior predictive hazard functions for 6 participants
newdata_prior = tibble(timebin = 6:15) %>% 
           expand_grid(pid = 1:6)

@@

```{r inspect-M0i}
model_M0i <- readRDS("Tutorial_2_Bayesian/models/model_M0i.rds")
summary(model_M0i)
formula(model_M0i)
plot(model_M0i)
```

@@

```{r inspect-M0c-prior}
model_M0c_prior <- readRDS("Tutorial_2_Bayesian/models/model_M0c_prior.rds")
```

@@

```{r ppc-model-M0c-prior, eval=F}
# Generate prior predictive hazard functions for 6 participants
# Specify
N_obs = 100 # increase for smoother results
set.seed(1)

@@

```{r post-M0i}
post <- as_draws_df(model_M1i) %>% 
  select(-lp__) %>% 
  as_tibble()

@@

```{r plot-post-M0i}
tidy_fixed <- post %>% 
  select(starts_with("b_"), .chain, .iteration, .draw) %>% 
  rename(chain=.chain, iter=.iteration, draw=.draw) %>% 
  pivot_longer(-c(chain, draw, iter)) %>% 
  mutate(timebin = str_sub(name,10,11),
         timebin = factor(str_remove(timebin,":"),levels=c(6:15)),
         condition = str_sub(name,17,18),
         condition = factor(str_remove(condition,"e"),
                            levels=c(1,2,3),
                            labels=c("blank","congruent","incongruent")))
head(tidy_fixed)
tail(tidy_fixed)

@@

```{r save-pred-grand, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pred_grand.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-pred-pid, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pred_pid.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-pred-pid-new, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pred_pid_new.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-grand-AMEs, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_grand_AME.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-pid-AMEs, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pid_AMEs.png", width = 10, height = 8, dpi = 800)
```

@@

```{r save-pid-new-AMEs, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pid_new_AMEs.png", width = 10, height = 8, dpi = 800)
```

@@

```{r props-contrasts}
pabove <- epreds_grand_diffs %>% 
  group_by(timebin,contrast) %>%
  summarize(prop_above = mean(pred_haz > 0)) %>% 
  arrange(contrast,timebin)

### 2024-11-24 Tutorial_2b.Rmd
update html and Rmd files
update tuts 2a and 2b

---
title: "Tutorial_2b"
author: "sven panis"
date: "2024-10-18"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

Content:
1. Load libraries.
2. Load and wrangle the person-trial data set that we saved in Tutorial 1a.
3. Fit a conditional accuracy model.
4. Display effects for the conditional accuracy model.

@@

# 2. Load and wrangle the person-trial data set that we saved in Tutorial 1a.

```{r load-data}
ca_data <- read_csv("Tutorial_1_descriptive_stats/data/inputfile_ca_modeling.csv")
print(ca_data,n=30)
summary(ca_data) # 2683 rows: 6 participants, trial, 3 conditions, 15 periods, and acc
```

@@

```{r prepare-data}
# select analysis time range: (200,600]
ca_data <- ca_data %>% filter(drt > 5)

# create factor condition, with "blank" as the reference level
ca_data <- ca_data %>% mutate(condition = factor(condition, labels = c("blank", "congruent","incongruent")))

# center TIME (period) on bin 9, and trial on trial 1000 and rescale.
ca_data <- ca_data %>% 
        mutate(period_9 = drt - 9,
               trial_c = (trial - 1000)/1000)

head(ca_data,n=17)
summary(ca_data)
# 6 subjects
# condition: blank (1303), congruent (668), incongruent (626)
# period_9: -3 to 6
# trial_c: -0.999 to 0.540
```

@@

We fit a single model "M4_ca": We use a third-order polynomical specification of TIME in the baseline condition (blank prime), and relax all assumptions for prime types, and trial number.

## Prepare data for M4_ca.

```{r data-M4-ca}
# remove unnecessary columns before fitting a model
M4_ca_data <- ca_data %>% select(-c(bl,tr,trial,drt)) # 2597 rows
head(M4_ca_data)
```

### Set up priors for M4_ca.

```{r priors-cloglog-M4-ca}
priors_M4_ca <- c(
  set_prior("normal(0,1)", class = "b"),       # weakly informative prior for beta parameters when using logit link
  set_prior("student_t(7.61, 0, 1.57)", class = "b", coef="Intercept"),      # weakly informative prior for Intercept when using logit link
  set_prior("normal(0, 1)", class = "sd"),                     # for standard deviation of random effects
  set_prior("lkj(2)", class = "cor")                           # for correlations between random effects
)
```

### Fit model M4_ca.

```{r fit-model-M4-ca, eval=F}
plan(multicore)

model_M4_ca <- 
   brm(data = M4_ca_data,
       family = binomial(link="logit"),
       acc | trials(1) ~ 0 + Intercept +
                          condition*period_9*trial_c + 
                          condition*period_9*I(trial_c^2) + 
                          condition*I(period_9^2)*trial_c +
                          condition*I(period_9^2)*I(trial_c^2) +
                          condition*I(period_9^3) +
                          trial_c*I(period_9^3) +
                          (1 +  condition*period_9*trial_c +
                                condition*period_9*I(trial_c^2) + 
                                condition*I(period_9^2)*trial_c +
                                condition*I(period_9^2)*I(trial_c^2) +
                                condition*I(period_9^3) +
                                trial_c*I(period_9^3) | pid),
       prior = priors_M4_ca,
       chains = 4, cores = 4, iter = 3000, warmup = 1000, 
       control = list(adapt_delta = 0.999, step_size = 0.04, max_treedepth = 14),
       seed = 12, init = "0",
       file = "Tutorial_2_Bayesian/models/model_M4_ca")
```

Model_M4_ca took about 7 hours to run.

```{r check-model-M4-ca, eval=F}
model_M4_ca <- readRDS("Tutorial_2_Bayesian/models/model_M4_ca.rds")
summary(model_M4_ca)
```

@@

```{r load-model-M4-ca}
model_M4_ca <- readRDS("Tutorial_2_Bayesian/models/model_M4_ca.rds")
```

@@

```{r pareto}
loo(model_M4_ca)$diagnostics %>% 
  data.frame() %>% 
  # attach the `id` values
  bind_cols(M4_ca_data) %>% 
  mutate(id = 1:n()) %>%

  ggplot(aes(x = id, y = pareto_k)) +
  geom_point(alpha = 3/4) + 
  geom_text(data = . %>% filter(pareto_k > .2),
            aes(x = id + 2, label = id),
            size = 3, hjust = 0) +
  theme(panel.grid = element_blank())
```

## Visualize posterior distributions of the effects of congruent and incongruent primes on logit-ca(t) relative to blank prime, for each time bin in trials 500, 1000, and 1500.

```{r post-distr}
get_variables(model_M4_ca)[1:31]

post <-as_draws_df(model_M4_ca) %>% # 8000 draws x 715 variables
   select(starts_with("b_")) %>%       # 8000 x 31
   expand_grid(period_9 = -3:6) %>%   
   mutate(period_9sq = period_9^2,
          period_9cu = period_9^3,
          trial500 = -500/1000,
          trial500sq = trial500^2,
          trial1500 = 500/1000,
          trial1500sq = trial1500^2)

# effects for trials 500, 1000, and 1500
effects <- post %>% 
  mutate(`congruent trial 1500` = b_conditioncongruent + period_9 * `b_conditioncongruent:period_9` + 
            period_9sq * `b_conditioncongruent:Iperiod_9E2` + period_9cu * `b_conditioncongruent:Iperiod_9E3` +
            trial1500 * `b_conditioncongruent:trial_c` + trial1500sq * `b_conditioncongruent:Itrial_cE2` +
            period_9 * trial1500 * `b_conditioncongruent:period_9:trial_c` +
            period_9sq * trial1500 * `b_conditioncongruent:trial_c:Iperiod_9E2` +
            period_9 * trial1500sq * `b_conditioncongruent:period_9:Itrial_cE2` +
            period_9sq * trial1500sq * `b_conditioncongruent:Itrial_cE2:Iperiod_9E2`,

         `incongruent trial 1500` = b_conditionincongruent + period_9 * `b_conditionincongruent:period_9` + 
            period_9sq * `b_conditionincongruent:Iperiod_9E2` + period_9cu * `b_conditionincongruent:Iperiod_9E3` +
            trial1500 * `b_conditionincongruent:trial_c` + trial1500sq * `b_conditionincongruent:Itrial_cE2` +
            period_9 * trial1500 * `b_conditionincongruent:period_9:trial_c` +
            period_9sq * trial1500 * `b_conditionincongruent:trial_c:Iperiod_9E2` +
            period_9 * trial1500sq * `b_conditionincongruent:period_9:Itrial_cE2` +
            period_9sq * trial1500sq * `b_conditionincongruent:Itrial_cE2:Iperiod_9E2`,

         `congruent trial 500` = b_conditioncongruent + period_9 * `b_conditioncongruent:period_9` + 
            period_9sq * `b_conditioncongruent:Iperiod_9E2` + period_9cu * `b_conditioncongruent:Iperiod_9E3` +
            trial500 * `b_conditioncongruent:trial_c` + trial500sq * `b_conditioncongruent:Itrial_cE2` +
            period_9 * trial500 * `b_conditioncongruent:period_9:trial_c` +
            period_9sq * trial500 * `b_conditioncongruent:trial_c:Iperiod_9E2` +
            period_9 * trial500sq * `b_conditioncongruent:period_9:Itrial_cE2` +
            period_9sq * trial500sq * `b_conditioncongruent:Itrial_cE2:Iperiod_9E2`,

         `incongruent trial 500` = b_conditionincongruent + period_9 * `b_conditionincongruent:period_9` +
            period_9sq * `b_conditionincongruent:Iperiod_9E2` + period_9cu * `b_conditionincongruent:Iperiod_9E3` +
            trial500 * `b_conditionincongruent:trial_c` + trial500sq * `b_conditionincongruent:Itrial_cE2` +
            period_9 * trial500 * `b_conditionincongruent:period_9:trial_c` +
            period_9sq * trial500 * `b_conditionincongruent:trial_c:Iperiod_9E2` +
            period_9 * trial500sq * `b_conditionincongruent:period_9:Itrial_cE2` +
            period_9sq * trial500sq * `b_conditionincongruent:Itrial_cE2:Iperiod_9E2`,

         `congruent trial 1000` = b_conditioncongruent + period_9 * `b_conditioncongruent:period_9` + 
            period_9sq * `b_conditioncongruent:Iperiod_9E2` + period_9cu * `b_conditioncongruent:Iperiod_9E3`,

         `incongruent trial 1000` = b_conditionincongruent + period_9 * `b_conditionincongruent:period_9` +
            period_9sq * `b_conditionincongruent:Iperiod_9E2` + period_9cu * `b_conditionincongruent:Iperiod_9E3`) 
```

```{r plot-effects}
plot_facet <- effects %>%
  pivot_longer(cols=`congruent trial 1500`:`incongruent trial 1000`, names_to = "condition" ) %>%
  select(condition, period_9, value) %>%
  group_by(period_9) %>%

  ggplot(aes(x = period_9, y = value)) +
  stat_lineribbon(point_interval = mean_hdi,.width = c(0.5, 0.8, 0.95),show.legend=T) +
  scale_fill_brewer() +
  geom_hline(yintercept=0, linetype="dashed", color = "red") +
  scale_x_continuous(breaks = c(-3:6), labels=c(((-3:6)+9)*40),
                     limits = c(-3,6)) +
  scale_y_continuous(breaks = c(-50,-40,-30,-20,-10,0,10,20,30,40,50), limits = c(-50,50)) +
  labs(x = "time bin", y = "logit-ca") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90),
        panel.background = element_rect(fill="white", color="black"),
        legend.position = "top") +
  facet_wrap(~ factor(condition,levels=c("congruent trial 500","congruent trial 1000","congruent trial 1500","incongruent trial 500","incongruent trial 1000","incongruent trial 1500")))

plot_facet
```

```{r save-plot-effects, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4_ca_effects_con_incon_3trials.png", width = 8, height = 8, dpi = 300)
```

## calculate point and interval estimates, and odds ratios.

```{r table-interval-estimates}
int_c_500 <- effects %>%
  select(`congruent trial 500`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `odds ratio` = exp(`congruent trial 500`),
         mean = `congruent trial 500`,
         condition = "c500") %>%
  select(bin_endpoint,condition, mean, .lower, .upper, .width, `odds ratio`)

int_i_500 <- effects %>%
  select(`incongruent trial 500`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `odds ratio` = exp(`incongruent trial 500`),
         mean = `incongruent trial 500`,
         condition = "i500") %>%
  select(bin_endpoint, condition,mean, .lower, .upper, .width, `odds ratio`)

int_c_1000 <- effects %>%
  select(`congruent trial 1000`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `odds ratio` = exp(`congruent trial 1000`),
         mean = `congruent trial 1000`,
         condition = "c1000" ) %>%
  select(bin_endpoint,condition,mean, .lower, .upper, .width, `odds ratio`)

int_i_1000 <- effects %>%
  select(`incongruent trial 1000`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `odds ratio` = exp(`incongruent trial 1000`),
         mean = `incongruent trial 1000`,
         condition = "i1000") %>%
  select(bin_endpoint, condition,mean, .lower, .upper, .width,`odds ratio`)

int_c_1500 <- effects %>%
  select(`congruent trial 1500`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `odds ratio` = exp(`congruent trial 1500`),
         mean = `congruent trial 1500`,
         condition = "c1500" ) %>%
  select(bin_endpoint, condition, mean, .lower, .upper, .width, `odds ratio`)

int_i_1500 <- effects %>%
  select(`incongruent trial 1500`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `odds ratio` = exp(`incongruent trial 1500`),
         mean = `incongruent trial 1500`,
         condition = "i1500") %>%
  select(bin_endpoint, condition,mean, .lower, .upper, .width,  `odds ratio`)

test <- rbind(int_c_500, int_c_1000, int_c_1500,int_i_500,int_i_1000, int_i_1500)
test %>% print(n=60)
```

```{r save-table-interval-estimates, eval=F}
write_csv(test, file="Tutorial_2_Bayesian/tables/ca_effects_intervals_table.csv")
```

## Plot model-based predicted logit-ca(t) and ca(t) functions, for a single subject.

```{r select-pid}
selected_subject = 6 # select pid here (1:6) manually
```

```{r help-function}
make_fitted <- function(fit, scale, ...) {

  fitted(fit,
         newdata = nd,
         scale = scale,
         ...) %>% 
    data.frame() %>% 
    bind_cols(nd)
}
```

### Set up new data.

```{r new-data}
# define the `newdata`
nd <- tibble(pid = 1:6) %>%
  expand_grid(incon = 0:1,
                con  = 0:1,
                trial_c = c(-0.5,0,0.5),
                period_9 = -3:6) %>%
  filter(!(con ==1 & incon == 1)) %>%
  mutate(Iperiod_9E2 = period_9^2,
         Iperiod_9E3 = period_9^3,
         Itrial_cE2 = trial_c^2,
         condition = ifelse(con==1 & incon==0,"congruent",
                     ifelse(con==0 & incon==1,"incongruent", "blank")),
         condition = factor(condition, levels=c("blank" ,"congruent","incongruent"))) 
```

### First, on the logit-ca(t) scale.

```{r subject-logit}
make_fitted(model_M4_ca, scale = "linear") %>% 
  mutate(cond   = rep(rep(c("N","C","I"),each=30),6),
         trial  = factor(trial_c,levels=c(-0.5,0.0,0.5),labels=c("trial 500","trial 1000","trial 1500")),
         period = period_9+9) %>% 
  filter(pid==selected_subject) %>% 
  # plot
  ggplot(aes(x = period, y = Estimate, ymin = Q2.5, ymax = Q97.5,
             fill = condition, color = condition)) +
  geom_ribbon(alpha = 1/5, linewidth = 0) +
  geom_line() +
  scale_fill_viridis_d(NULL, option = "A", end = .6, direction = -1) +
  scale_color_viridis_d(NULL, option = "A", end = .6, direction = -1) +
  scale_x_continuous("time bin endpoint", breaks = 6:15, limits = c(6, 15), labels=c(6:15)*40) +
  ylab("fitted logit(ca)") +
  coord_cartesian(ylim = c(-20, 20)) +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill="white",color="black"),
        legend.position = "top",
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~ trial)
```

### Second, on the ca(t) scale.

```{r subject-ca}
make_fitted(model_M4_ca, scale = "response") %>% 
  mutate(cond   = rep(rep(c("N","C","I"),each=30),6),
         trial  = factor(trial_c,levels=c(-0.5,0.0,0.5),labels=c("trial 500","trial 1000","trial 1500")),
         period = period_9+9) %>% 
  filter(pid==selected_subject) %>% 
  # plot
  ggplot(aes(x = period, y = Estimate, ymin = Q2.5, ymax = Q97.5,
             fill = condition, color = condition)) +
  geom_ribbon(alpha = 1/5, linewidth = 0) +
  geom_line() +
  scale_fill_viridis_d(NULL, option = "A", end = .6, direction = -1) +
  scale_color_viridis_d(NULL, option = "A", end = .6, direction = -1) +
  scale_x_continuous("time bin endpoint", breaks = 6:15, limits = c(6, 15), labels=c(6:15)*40) +
  ylab("fitted ca(t)") +
  coord_cartesian(ylim = c(0, 1)) +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill="white",color="black"),
        legend.position = "top",
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~ trial)
```

```{r save-plot-fit-hazard, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4_ca_effects_subject6.png", width = 10, height = 10, dpi = 300)
```

>>>>

---
title: "Tutorial_2b"
author: "sven panis"
date: "2024-10-18"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: united
editor_options: 
  chunk_output_type: console
---

@@

@@

theme settings for ggplot

```{r plot-settings, results='hide'}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 22, face = "bold"), 
          title = element_text(size = 22, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# 2. Load and wrangle the person-trial data set.

```{r load-data, results='hide'}
ca_data <- read_csv("Tutorial_1_descriptive_stats/data/inputfile_ca_modeling.csv")
head(ca_data)
```

@@

```{r prepare-data}
# select analysis time range: (200,600]
ca_data <- ca_data %>% filter(drt > 5) %>%

# create factor condition, with "blank" as the reference level
mutate(condition = factor(condition, 
                          labels = c("blank", "congruent","incongruent")),
       prime = ifelse(condition=="blank",1, ifelse(condition=="congruent",2,3)),
      prime = factor(prime,levels=c(1,2,3)),
       timebin = factor(drt, levels=c(6:15)),
       period_9 = drt - 9,
       trial_c = (trial - 1000)/1000)

head(ca_data)
```

@@

We fit a single model "M1i_ca", using index coding for both TIME and condition (variables "timebin" and "prime" in ca_data).

## Prepare data for M1i_ca.

```{r data-M1i-ca}
# remove unnecessary columns before fitting a model
data_M1i_ca <- ca_data %>% select(pid,acc,timebin,prime)
head(data_M1i_ca)
```

## Set up priors for M1i_ca.

```{r priors-cloglog-M1i-ca}
priors_M1i_ca <- c(
  set_prior("student_t(7.61, 0, 1.57)", class = "b"), # use flat prior on logit scale for the proportion ca 
  set_prior("normal(0, 1)", class = "sd"),                    
  set_prior("lkj(2)", class = "cor")                        
)
```

## Fit model M1i_ca.

```{r fit-model-M1i-ca, eval=F}
plan(multicore)

model_M1i_ca <- 
   brm(data = data_M1i_ca,
       family = bernoulli(link="logit"),  # use logit link for conditional accuracy
       formula = acc ~ 0 + timebin:prime  +
                        (0 + timebin:prime | pid),
       prior = priors_M1i_ca,
       chains = 4, cores = 4, iter = 3000, warmup = 1000, 
       control = list(adapt_delta = 0.999, step_size = 0.04, max_treedepth = 14),
       seed = 12, init = "0",
       file = "Tutorial_2_Bayesian/models/model_M1i_ca")
```

Model_M1i_ca took about 11 minutes to run.

```{r inspect-M1i-ca}
model_M1i_ca <- readRDS("Tutorial_2_Bayesian/models/model_M1i_ca.rds")
fixef(model_M1i_ca)
```

@@

@@

```{r pareto}
loo(model_M1i_ca)$diagnostics %>% 
  data.frame() %>% 
  # attach the `id` values
  bind_cols(data_M1i_ca) %>% 
  mutate(id = 1:n()) %>%
  ggplot(aes(x = id, y = pareto_k)) +
  geom_point(alpha = 3/4) + 
  geom_text(data = . %>% filter(pareto_k > .2),
            aes(x = id + 2, label = id),
            size = 3, hjust = 0) +
  theme(panel.grid = element_blank())
```

## Plot posterior distributions for M1i_ca.

Wrangle the posterior draws.

```{r post-M0i}
post_ca <- as_draws_df(model_M1i_ca) %>% 
  select(-lp__) %>% 
  as_tibble()

post_summary <- posterior_summary(model_M1i_ca, robust = TRUE)
post_summary[1:30,]

post_qi_b <- post_ca %>%
  select(starts_with("b_")) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>% 
  median_qi(value) %>% 
  arrange(name)
head(post_qi_b) # 30 "fixed" effects 
```

Visualise fixed effects.

```{r plot-post-M0i-ca}
tidy_fixed_ca <- post_ca %>% 
  select(starts_with("b_"), .chain, .iteration, .draw) %>% 
  rename(chain=.chain, iter=.iteration, draw=.draw) %>% 
  pivot_longer(-c(chain, draw, iter)) %>% 
  mutate(timebin = str_sub(name,10,11),
         timebin = factor(str_remove(timebin,":"),levels=c(6:15)),
         condition = str_sub(name,17,18),
         condition = factor(str_remove(condition,"e"),
                            levels=c(1,2,3),
                            labels=c("blank","congruent","incongruent")))
head(tidy_fixed_ca)
tail(tidy_fixed_ca)

# plot
p_tidy_fixed_ca <- ggplot(tidy_fixed_ca, aes(x = timebin, y = value, fill=condition)) +  
  stat_halfeye(alpha=0.7) +
  labs(title = 'Posterior distributions for "fixed" effects\nin Model M1i_ca',
       x = "time bin", 
       y = "logit-ca") +
  scale_fill_brewer(palette = "Dark2") +
  scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
  scale_y_continuous(limits=c(-10,10)) +
  theme(axis.text.x = element_text(angle=90)) +
  facet_wrap(~condition)
p_tidy_fixed_ca
```

```{r save-post, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_ca_postdistr.png", width = 10, height = 8, dpi = 800)
```

## Plot predicted conditional accuracy functions

### Grand mean

```{r epred-grand}
dat_M1i_ca <- as_tibble(model_M1i_ca$data)

epreds_grand <- dat_M1i_ca %>% 
  data_grid(timebin, prime) %>% 
  add_epred_draws(model_M1i_ca, 
                  re_formula = NA) %>% 
  mutate(prime = factor(prime, 
                        levels=c(1,2,3),
                        labels=c("blank","congruent","incongruent"))) %>%
  ungroup()
```

Summarize and plot predicted hazard values.

```{r epred-grand-summary}
epreds_grand %>% 
  group_by(timebin,prime) %>% 
  mean_qi()
```

```{r epred-grand-plot}
 ggplot(epreds_grand, aes(x=timebin, y=.epred, 
                          fill=prime, color=prime)) +
    stat_lineribbon(alpha = 0.5, .width = .95) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(y = "predicted conditional accuracy") +
    ggtitle("Average participant")
```

```{r save-epred-grand, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_ca_pred_grand.png", width = 10, height = 8, dpi = 800)
```

### Subject-specific

```{r epred-pid}
epreds_pid <- dat_M1i_ca %>% 
  data_grid(pid,timebin, prime) %>% 
  add_epred_draws(model_M1i_ca, 
                  re_formula = NULL) %>% 
  mutate(prime = factor(prime, 
                        levels=c(1,2,3),
                        labels=c("blank","congruent","incongruent"))) %>%
  ungroup()
```

Summarize and plot predicted hazard values.

```{r epred-pid-summary}
epreds_pid %>% 
  group_by(pid,timebin,prime) %>% 
  mean_qi()
```

```{r plot-epred-pid}
 ggplot(epreds_pid, aes(x=timebin, y=.epred, 
                       fill=prime, color=prime)) +
    stat_lineribbon(alpha = 0.5, .width = .95) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(y = "predicted conditional accuracy") +
    ggtitle("Each participant (N = 6)") +
    facet_wrap(~pid, ncol=3)
```

```{r save-epred-pid, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_ca_pred_pid.png", width = 10, height = 8, dpi = 800)
```

## Plot average marginal effects (AMEs)

### Grand mean AMEs

```{r grand-ame}
epreds_grand_diffs <- epreds_grand %>%
  pivot_wider(id_cols = c(timebin, .draw),
              names_from = "prime",
              values_from = ".epred") %>% #80000 x 5
  mutate(`congruent minus blank` = congruent - blank,
         `incongruent minus blank` = incongruent -  blank) %>% 
  select(-c(blank,congruent,incongruent)) %>% 
  pivot_longer(cols = c(`congruent minus blank`,`incongruent minus blank`),
               names_to = "contrast",
               values_to = "pred_ca")

epreds_grand_diffs # 160 000 rows 
```

Summarize and plot.

```{r grand-ame-summary}
table <- epreds_grand_diffs %>%
  group_by(contrast,timebin) %>%
  mean_qi(.width = c(.95)) %>%
  arrange(contrast,timebin,.width) %>%
  select(-c(.width,.point,.interval))
```

```{r save-table-grand-AMEs, eval=F}
write_csv(table, file="Tutorial_2_Bayesian/tables/ca_grand_AMEs.csv")
```

```{r grand-ame-plot}
 ggplot(epreds_grand_diffs, aes(x=timebin, y=pred_ca, 
                       fill=contrast)) +
  stat_lineribbon(alpha = 0.5, 
                  point_interval = "mean_qi",
                  .width=c(.8,.95)) +
 # stat_halfeye(point_interval = "mean_qi",.width=c(.8,.95))+
  geom_hline(yintercept = 0, 
             color = "red", 
             lty = 3) +
  scale_y_continuous(limits=c(-1,1)) +
  scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme(axis.text.x = element_text(angle=90)) +
  labs(y = "difference in predicted ca") +
  ggtitle("Grand average marginal effect") +
  facet_wrap(~contrast)
```

```{r save-grand-AMEs, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_ca_grand_AME.png", width = 10, height = 8, dpi = 800)
```

### Subject-specific AMEs

To calculate the subject-specific AMEs for each time bin, we create contrasts between the conditional means.

```{r epred-pid-ame}
epreds_pid_diffs <- epreds_pid %>%
  pivot_wider(id_cols = c(pid,timebin, .draw),
              names_from = "prime",
              values_from = ".epred") %>% #80000 x 5
  mutate(`congruent minus blank` = congruent - blank,
         `incongruent minus blank` = incongruent -  blank) %>% 
  select(-c(blank,congruent,incongruent)) %>% 
  pivot_longer(cols = c(`congruent minus blank`,`incongruent minus blank`),
               names_to = "contrast",
               values_to = "pred_ca") 
epreds_pid_diffs # 160 000 rows 
```

Summarize and plot the contrasts in predicted hazard values.

```{r epred-pid-ame-summary}
epreds_pid_diffs %>% group_by(pid,timebin,contrast) %>% mean_qi()
```

```{r epred-pid-ame-plot}
 ggplot(epreds_pid_diffs, aes(x=timebin, y=pred_ca, 
                       fill=contrast, color=contrast)) +
    stat_lineribbon(alpha = 0.5, point_interval = "mean_qi",.width=c(.95)) +
    #stat_halfeye(point_interval = "mean_qi",.width=c(.8,.95)) +
    geom_hline(yintercept = 0, color = "red", lty = 3) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(-1,1)) +
    labs(y = "difference in predicted ca") +
    ggtitle("Subject-specific AMEs") +
    facet_wrap(~pid, ncol=3)
```

```{r save-pid-AMEs, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_ca_pid_AMEs.png", width = 10, height = 8, dpi = 800)
```
